---
title: "Practicum 2"
output: html_notebook
---


# Create the SQlite file 
```{r}
library(RSQLite)

fpath = "/Users/wangyichen/Desktop/"
dbfile = "Practicum2.sqlite"

dbcon <- dbConnect(RSQLite::SQLite(), paste0(fpath,dbfile))

```

# Set foreign key constraint on
```{sql connection=dbcon}
PRAGMA foreign_keys = ON
```

# Drop table Article if it exists
```{sql connection=dbcon}
DROP TABLE IF EXISTS Article
```

# Create Table Article
```{sql connection=dbcon}
CREATE TABLE Article(
   ArticleID INTEGER NOT NULL,
   JournalID INTEGER NOT NULL DEFAULT 0,
   AuthorListID INTEGER NOT NULL DEFAULT 0,
   PaginationID INTEGER NOT NULL DEFAULT 0,
   AbstractID INTEGER NOT NULL DEFAULT 0,
   Language VARCHAR(30),
   ArticleDateID INTEGER NOT NULL DEFAULT 0,
   ArticleTitle CARCHAR(30),
   PRIMARY KEY (ArticleID)
   FOREIGN KEY (JournalID) REFERENCES Journal (JournalID)
     ON DELETE SET DEFAULT
     ON UPDATE CASCADE
   FOREIGN KEY (AuthorListID) REFERENCES AuthorList (AuthorListID)
     ON DELETE SET DEFAULT
     ON UPDATE CASCADE
   FOREIGN KEY (PaginationID) REFERENCES Pagination (PaginationID)
     ON DELETE SET DEFAULT
     ON UPDATE CASCADE
   FOREIGN KEY (AbstractID) REFERENCES Abstract (AbstractID)
     ON DELETE SET DEFAULT
     ON UPDATE CASCADE
   FOREIGN KEY (ArticleDateID) REFERENCES ArticleDate (ArticleDateID)
     ON DELETE SET DEFAULT
     ON UPDATE CASCADE
)
```

# Drop Journal Table
```{sql connection=dbcon}
DROP TABLE IF EXISTS Journal
```

# Create Table Journal
```{sql connection=dbcon}
CREATE TABLE Journal(
   JournalID INTEGER NOT NULL,
   ISSNType TEXT NOT NULL,
   ISSN TEXT NOT NULL,
   JournalIssueID INTEGER NOT NULL,
   Title TEXT NOT NULL,
   ISO Abbreviation TEXT NOT NULL,
   PRIMARY KEY (JournalID)
   FOREIGN KEY (JournalIssueID) REFERENCES JournalIssue (JournalIssueID)
     ON DELETE CASCADE
     ON UPDATE CASCADE
)
```

# Drop Journal Issue Table
```{sql connection=dbcon}
DROP TABLE IF EXISTS JournalIssue
```

# Create Table Journal Issue
```{sql connection=dbcon}
CREATE TABLE JournalIssue(
   JournalIssueID INTEGER NOT NULL,
   CitedMedium TEXT NOT NULL,
   Volume INTEGER NOT NULL,
   Issue INTEGER NOT NULL,
   PubDateID INTEGER NOT NULL,
   PRIMARY KEY (JournalIssueID)
   FOREIGN KEY (PubDateID) REFERENCES JournalPubDate (PubDateID)
     ON DELETE CASCADE
     ON UPDATE CASCADE
)
```

# Create Table Pub Date
```{sql connection=dbcon}
CREATE TABLE JournalPubDate(
   PubDateID INTEGER NOT NULL,
   Year INTEGER NOT NULL,
   Month INTEGER NOT NULL,
   PRIMARY KEY (PubDateID)
)
```

# Drop Author Table
```{sql connection=dbcon}
DROP TABLE IF EXISTS Author
```

# Create Table Author List
```{sql connection=dbcon}
CREATE TABLE AuthorList(
   AuthorListID INTEGER NOT NULL,
   PRIMARY KEY (AuthorListID)
)
```

# Drop Author Details Table
```{sql connection=dbcon}
DROP TABLE IF EXISTS Author
```

# Create Table Author 
```{sql connection=dbcon}
CREATE TABLE Author(
   AuthorID INTEGER NOT NULL,
   LastName TEXT NOT NULL,
   FirstName TEXT NOT NULL,
   Initals TEXT NOT NULL,
   Affilication TEXT NOT NULL,
   PRIMARY KEY (AuthorID)
)

```

# Drop History Table
```{sql connection=dbcon}
DROP TABLE IF EXISTS History
```

# Create Table History
```{sql connection=dbcon}
CREATE TABLE HistoryPubInfo(
   PubMedPubDateID INTEGER NOT NULL,
   HistoryPubInfoID INTEGER NOT NULL,
   ArticleID INTEGER NOT NULL,
   PRIMARY KEY (HistoryPubInfoID)
   FOREIGN KEY (PubMedPubDateID) REFERENCES PubMedPubDate (PubMedPubDateID)
     ON DELETE CASCADE
     ON UPDATE CASCADE
   FOREIGN KEY (ArticleID) REFERENCES Article (ArticleID)
     ON DELETE CASCADE
     ON UPDATE CASCADE
)

```

# Drop Pub Date Table
```{sql connection=dbcon}
DROP TABLE IF EXISTS PubDetails
```

# Create Table PubDate
```{sql connection=dbcon}
CREATE TABLE PubMedPubDate(
   PubMedPubDateID INTEGER NOT NULL,
   PubStatus TEXT NOT NULL,
   Year INTEGER NOT NULL,
   Month INTEGER NOT NULL,
   Day INTEGER NOT NULL,
   PRIMARY KEY (PubDetailsID)
)
```
















# Part 3 starts from here

# Load Libraries for parsing
```{r loadLibraries}
library(XML)

library(RSQLite)
library(DBI)
library(knitr)
```

# Set up filenames and paths
```{r filenames}
path <- "/Users/wangyichen/Desktop/Practicum2/"
fn <- "pubmed_sample.xml"
fpn = paste0(path, fn)
dbfn <- "practicum2.db"
dbfpn = paste0(path, dbfn)
```

# Load XML into Document Object Model (DOM)
```{r}
# Reading the XML file and parse into DOM
xmlDOM <- xmlParse(file = fpn)

# get the root node of the DOM tree
r <- xmlRoot(xmlDOM)
```

# Create the internal dataframe
```{r createDFs}
# Count the number of children node
numArticle <- xmlSize(r)

# Create various data frames to hold data
Article.df <- data.frame (ArticleID = vector (mode = "integer", length = numArticle),
                          PMID = vector(mode = "integer", length = numArticle),
                          PubModel = vector(mode = "character", length = numArticle),
                          ArticleTitle = vector(mode = "character", length = numArticle),
                          AuthorListID = vector(mode = "integer", length = numArticle),
                          HistoryID = vector(mode = "integer", length = numArticle),
                          stringAsFactors = F
                          )
                          

Journal.df <- data.frame(JournalID = vector(mode = "integer", length = numArticle),
                         ISSNType = vector(mode = "character", length = numArticle),
                         ISSN = vector(mode = "character", length = numArticle),
                         JournalIssueID = vector(mode = "integer", length = numArticle),
                         Title = vector(mode = "character", length = numArticle),
                         ISOAbbreviation = vector(mode = "character", length = numArticle),
                         stringsAsFactors = F
                         )

JournalIssue.df <- data.frame(JournalIssueID = vector(mode = "integer", length = numArticle),
                              CitedMedium = vector(mode = "character", length = numArticle),
                              Volume = vector(mode = "integer", length = numArticle),
                              Issue = vector(mode = "integer", length = numArticle),
                              PubDateID = integer(),
                              stringsAsFactors = F
                              )

PubDate.df <- data.frame(PubDateID = integer(),
                         Year = integer(),
                         Date = integer(),
                         stringsAsFactors = F
                         )

AuthorList.df <- data.frame(AuthorListID = vector(mode = "integer", length = numArticle),
                            AuthorID = integer(),
                            stringsAsFactors = F
                            )

History.df <- data.frame(HistoryID = vector(mode = "integer", length = numArticle),
                         PubDetailsID = vector(mode = "integer", length = numArticle),
                         stringsAsFactors = F
                         )

PubDetails.df <- data.frame(PubDetailsID = vector(mode = "integer", length = numArticle),
                            PubStatus = character(),
                            Year = integer(),
                            Month = integer(),
                            Day = integer(),
                            stringsAsFactors = F
                            )

```
